### 2024-04-19 docs/SOSP 2024/reduction.tex
switch to python style loops to save space

The MIR generated by \Treebeard{} for the above schedule is as follows. 
\begin{lstlisting}[style=c++]
  float result[batch_size]
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2 {
    for t1 = 0 to N_t/2 {
      for batch = 0 to batch_size {
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(result[batch], p)
      }
    }
  }  
\end{lstlisting}

@@

\begin{lstlisting}[style=c++]
  float result[batch_size], partResults[2][batch_size]
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2 {
    for t1 = 0 to N_t/2 {
      for batch = 0 to batch_size {
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(partResults[t0/(N_t/2)][batch], p)
      }
    }
  }
  results = reduceDimension(partResults[:, :], 0)
\end{lstlisting}

>>>>

The MIR generated by \Treebeard{} for the above schedule is as follows. 
\begin{lstlisting}[style=c++]
  float result[batch_size]
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2:
    for t1 = 0 to N_t/2:
      for batch = 0 to batch_size:
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(result[batch], p)
\end{lstlisting}

@@

\begin{lstlisting}[style=c++]
  float result[batch_size], partResults[2][batch_size]
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2:
    for t1 = 0 to N_t/2:
      for batch = 0 to batch_size:
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(partResults[t0/(N_t/2)][batch], p)

  results = reduceDimension(partResults[:, :], 0)
\end{lstlisting}
